---
title: "nRMSE supplemental figure"
author: "Sahil Shah"
date: "9/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(cowplot)
```

Values to create nRMSE plot of accepted deleterious mutations
```{r}

nrmse_ratios <- c(0.5002038733810914, 0.4984854031362939, 0.4717189300202526, 0.03286139689848213, 0.04466259779355728, 0.022548489894631128)
betas <- c(0.001, 0.01, 0.1, 1.0, 1.3, 2.0)
nrmse_sd <- c(0.1667346244603638, 0.15763492542579308, 0.1491706234281576, 0.01039168612939965, 0.014123553524765173, 0.007130458586432446)

```

Create bar plot of the number of accepted deleterious mutations
```{r}

df <- data.frame(betas, nrmse_ratios)
df$betas <- format(df$betas, scientific = FALSE)

nrmse_bar <- df %>% ggplot(aes(x=as.character(betas), y=nrmse_ratios)) + 
  geom_bar(stat='identity', fill="grey", color="grey", width=0.75) + 
  theme_cowplot() + 
  xlab("Beta values") + 
  ylab("Fraction of deleterious accepted mutations") +
  scale_y_continuous(limits = c(0, 0.75), expand = c(0,0)) +
  geom_errorbar(aes(ymin=nrmse_ratios-nrmse_sd, ymax=nrmse_ratios+nrmse_sd), width=0.2) +
  theme(legend.position = "none")

nrmse_bar <- arrangeGrob(nrmse_bar, top=textGrob("B", x = unit(0.01, "npc"), y=unit(1.3, "npc"), just=c("left","top"), gp=gpar(col="black", font="bold", fontsize=20, fontfamily="Arial")))

```

Create scatterplot of nRMSE value for each accepted mutation
```{r}

nrmse_plots <- list()

for(rep in c(107, 115, 130, 131, 145, 152)){
  if(rep == 107){
    beta <- "0.001"
  }else if(rep == 115){
    beta <- "0.010"
  }else if(rep==130){
    beta <- "0.100"
  }else if(rep == 131){
    beta <- "1.000"
  }else if(rep == 145){
    beta <- "1.300"
  }else if(rep == 152){
    beta <- "2.000"
  }
  
  nrmse <- read.table(paste0("../../manuscript_results/SI_Fig_evaluating_nRMSE/paper_data1_rep", rep, "_nmut10/final/rmse_data.tsv"), 
                     header=TRUE)
  nrmse <- nrmse %>% filter(Accepted=='yes')
  if(!(5000 %in% nrmse$Iteration)){
    nrmse <- nrmse %>% add_row(Iteration=5000, NRMSE=nrmse$NRMSE[length(nrmse$NRMSE)], Accepted="yes")
  }
  if(rep != 152){
  nrmse_line_plot <- ggplot(nrmse, aes(x=Iteration, y=NRMSE)) + 
    geom_point(stat='identity', color='#D55E00', size=1) + 
    geom_line(size=1, stat='identity', color='#D55E00') + 
    theme_cowplot() +
    ylab("Root mean square error") +
    scale_y_continuous(limits = c(0, 3.5), expand = c(0, 0)) +
    scale_x_continuous(limits = c(0, 5100), expand = c(0, 0)) +
    panel_border(size=1, color="dark grey") +
    theme(legend.position = "none",
          axis.title = element_blank(),
          axis.ticks.x = element_blank(),
          axis.line.x = element_blank(),
          axis.text.x = element_blank())
  }else{
  nrmse_line_plot <- ggplot(nrmse, aes(x=Iteration, y=NRMSE)) +
    geom_point(stat='identity', color='#D55E00', size=1) + 
    geom_line(size=1, stat='identity', color='#D55E00') + 
    theme_cowplot() +
  xlab("Generation") + 
  ylab("Root mean square error") +
  scale_y_continuous(limits = c(0, 3.5), expand = c(0, 0)) +
  scale_x_continuous(limits = c(0, 5100), expand = c(0, 0)) +
  panel_border(size=1, color="dark grey") +
  theme(legend.position = "none",
        axis.title.y = element_blank())
  }
  
  nrmse_line_plot <- arrangeGrob(nrmse_line_plot, top=textGrob(paste0("beta = ", beta), 
                                                                  x = unit(0.65, "npc"), y=unit(0.8, "npc"),
                                                                  just=c("left","top"), 
                                                                  gp=gpar(col="black", font="bold", fontsize=15,
                                                                          fontfamily="Arial")))   

  
  nrmse_plots[[length(nrmse_plots) + 1]] <- nrmse_line_plot
}

```
Determines the beta values over each generation
```{r}

#Set the values for the x and y-axes
generations <- c(1:5000)

slope1 <- (1.1 - 1e-2) / (0.8 * 5000)
beta_val1 <- (slope1 * (generations[501:4500] - 500)) + 1e-2

slope2 <- (1.3 - 1.1) / (0.1 * 5000)
beta_val2 <- (slope2 * (generations[4501:5000] - 4500)) + 1.1

beta <- c(rep(0.01, 500), beta_val1, beta_val2)

```
Plots the beta values over each generation and saves it
```{r}

fitness_landscape <- data.frame(generations, beta)
beta_plot <- fitness_landscape %>% ggplot(aes(x=generations, y=beta)) + 
  geom_line(size=1, stat='identity', color='#000000') + 
  theme_cowplot() +
  xlab("Generation") + 
  ylab("Beta value (log scale)") + 
  panel_border(size=1, color="dark grey") +
  scale_y_log10() +
  theme(legend.position = "none",
        plot.title = element_blank())

beta_plot <- arrangeGrob(beta_plot, top=textGrob("C", x = unit(0, "npc"), y=unit(1.3, "npc"), just=c("left","top"), gp=gpar(col="black", font="bold", fontsize=20, fontfamily="Arial")))
```

Save nRMSE figure
```{r}

nrmse_supp <- grid.arrange(nrmse_plots[[1]], nrmse_plots[[2]], nrmse_plots[[3]], nrmse_plots[[4]], nrmse_plots[[5]], nrmse_plots[[6]], nrmse_bar, beta_plot, layout_matrix=rbind(cbind(c(1,2,3,4,5,6), c(7)), c(8)), left=textGrob("Normalized RMSE", gp=gpar(fontsize=15), rot=90, y=unit(0.6, "npc")), top=textGrob("A",just=c("left","top"), x = unit(-0.01, "npc"), y=unit(0.4, "npc"), gp=gpar(col="black", font="bold", fontsize=20,fontfamily="Arial")), heights=c(1,1,1,1,1,1.35,2,1))

ggsave("../../figure_output/figure_nrmse/nrmse_supplemental.png", nrmse_supp, height=12, width=9, limitsize=FALSE, units="in")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
